### 2015-03-10 ResearchNotes/Notes.Rmd
Added a few more variables, Loaded HUD data and added to bibliography.
Added the new HUD data and have the variable names, but not the recodes, for the variables I want to use.

#END on LINE 240

#Starting again from the bottom
#May need to do some editing on this.  Low values are too low
summary(RECS$KWH)/12

@@

#Get income working two ways
#MONEYPY row 789 in category then make cont.
RECS$MONEYPY<-revalue(as.factor(RECS$MONEYPY),c("1"="Less2500", "2"="Less5K", "3"="Less7500","4"="Less10K","5"="Less15K","6"="Less20K","7"="Less25K","8"="Less30K", "9"="Less35K","10"="Less40K","11"="Less45K","12"="Less50K","13"="Less55K","14"="Less60","15"="Less65","16"="Less70","17"="Less75","18"="Less80", "19"="Less85", "20"="Less90","21"="Less95","22"="Less100K","23"="Less120K","24"="Gr120K"))
summary(RECS$MONEYPY)

#RENTHELP
FOODASST

@@

# Restrict to primary and not seasonal 
```
Checkign out the weight variable
```{r}
summary(RECS$NWEIGHT)

@@

>>>>

##Start Recoding HERE
summary(RECS$AGECDRYER)
summary(RECS$TVCOLOR)
summary(RECS$TVTYPE1)
summary(RECS$TVONWD1)
summary(RECS$NUMPC)
summary(RECS$TIMEON1)
summary(RECS$WELLPUMP)
summary(RECS$EQUIPM)
summary(RECS$FUELHEAT)
summary(RECS$EQUIPAGE)
summary(RECS$TEMPHOME)
summary(RECS$TEMPGONE)
summary(RECS$TEMPNITE)
summary(RECS$H2OTYPE1)
summary(RECS$FUELH2O)
summary(RECS$WHEATSIZ)
summary(RECS$WHEATAGE)
summary(RECS$AIRCOND)
summary(RECS$COOLTYPE)
summary(RECS$CENACHP)
summary(RECS$AGECENAC)
summary(RECS$USECENAC)
summary(RECS$TEMPHOMEAC)
summary(RECS$TEMPGONEAC)
summary(RECS$TEMPNITEAC)
summary(RECS$NUMBERAC)
summary(RECS$WWACAGE)
summary(RECS$ESWWAC)
summary(RECS$USEWWAC)
summary(RECS$SWIMPOOL)
summary(RECS$POOL)
summary(RECS$FUELPOOL)
summary(RECS$RECBATH)
summary(RECS$FUELTUB)
summary(RECS$TYPEGLASS)
summary(RECS$ELCOOL)
summary(RECS$ELWARM)
summary(RECS$ELWATER)

summary(RECS$ELFOOD)

#May need to do some editing on this.  Low values are too low
summary(RECS$KWH)/12

@@

#Get income working two ways
#MONEYPY 
RECS$MONEYPY<-revalue(as.factor(RECS$MONEYPY),c("1"="Less2500", "2"="Less5K", "3"="Less7500","4"="Less10K","5"="Less15K","6"="Less20K","7"="Less25K","8"="Less30K", "9"="Less35K","10"="Less40K","11"="Less45K","12"="Less50K","13"="Less55K","14"="Less60","15"="Less65","16"="Less70","17"="Less75","18"="Less80", "19"="Less85", "20"="Less90","21"="Less95","22"="Less100K","23"="Less120K","24"="Gr120K"))
summary(RECS$MONEYPY)

RECS$RENTHELP<-revalue(as.factor(RECS$RENTHELP),c("0"=FALSE, "1"=TRUE, "-2"=FALSE))
summary(RECS$RENTHELP)

RECS$FOODASST<-revalue(as.factor(RECS$FOODASST),c("0"=FALSE, "1"=TRUE))
summary(RECS$FOODASST)

@@

```
Checkign out the weight variable
```{r}
summary(RECS$NWEIGHT)

@@

This is the data ME created from the HUD report on the number of complaints per 100K population

```{r}
HUD <- read.csv("~/Research/EnergyEthnicity/Data/HUD.csv")

#And the clean up from importing from excell
HUD$pop<-as.numeric(gsub(",","",HUD$pop))
summary(HUD)
```

```{r}
as.numeric(HUD$Pop)
```
